UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/experiments.tex
Minor edits.
update

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.

@@

\newpage

@@

   \includegraphics[width=1.7in]{flickr_cmp} &
   \includegraphics[width=1.7in]{cgan_cmp} &
   \includegraphics[width=1.7in]{ugan_cmp} &
   \includegraphics[width=1.7in]{uganp_cmp} \\ [-11ex]

@@

>>>>

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure. Laplacian stuff \cite{pertuz2013analysis}

@@

%\newpage

@@

   \includegraphics[width=1.7in]{flickr_cmp} &
   \includegraphics[width=1.7in]{cgan_cmp} &
   \includegraphics[width=1.7in]{ugan_cmp} &
   \includegraphics[width=1.7in]{uganp_cmp} \\ [-2ex]

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Gradient Difference Loss Metrics}
\begin{tabular}{| c | c | c | c | }
   \hline
   Patch/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   Red    & 11.53 & 9.39 & 10.93  \\ \hline
   Blue   & 7.52  & 4.83 &  5.50\\ \hline
   Green  & 4.15  & 3.18 & 3.25 \\ \hline
   Orange & 6.72  & 5.65 & 5.79 \\ \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\end{table}
